---
title: "Project1"
author: "DM"
date: "20/10/2020"
output: html_document
---

Codigo para leer datos que fueron descargados en la biblioteca Documents local

```{r}
library(tidyverse)

datos <- read_csv("activity.csv")

```

What is mean total number of steps taken per day?
For this part of the assignment, you can ignore the missing values in the dataset.


1. Calculate the total number of steps taken per day
2. If you do not understand the difference between a histogram and a barplot, research the difference between them. Make a histogram of the total number of steps taken each day
3. Calculate and report the mean and median of the total number of steps taken per day

Numero total de pasos por dia
```{r}
total_steps_per_day <- datos %>% filter(steps>=0) %>% select(date,steps) %>% group_by(date) %>% 
    summarize(total_steps=sum(steps))

#TOTAL DE PASOS POR DIA
total_steps_per_day
#Histograma
hist(total_steps_per_day$total_steps)

#Informe que calcula la media, mediana de pasos por dia
mean(total_steps_per_day$total_steps)

median(total_steps_per_day$total_steps)


```

